Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-08 manuscript.tex
8 updates

When searching for small-mass exoplanets using the RV technique, it is crucial to get the best precision possible on the determination of the RV, but also to measure precisely the shape variations of the CCF, as such variations are induced by stellar activity, and not by planets. The correlations between the width of the CCF and the RV, and the asymmetry of the CCF and the RV are used as a way to assess if the measurements are affect by stellar activity signals, therefore, the stronger those correlations are, the better we can probe low level of stellar activity.

>>>>

When searching for low-mass exoplanets using the RV technique, it is necessary to get precise estimates of the RV and also to account for variations induced by stellar activity in order to avoid false detections.  Stellar activity such as spots and faculae can lead to shape variations in the spectra features, which then results in shape variations of the CCF.
The correlations between the width or asymmetry of the CCF and the estimated RV are commonly used as way to detect if the RVs are affected by stellar activity signals.   Because the presence of real planets would result in only a shift in the CCF (not a shape change), strong correlations between the shape features of the CCF and the estimated RVs suggest that stellar activity may be present.
